A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-07-01 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.

Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals. For a detailed discussion of the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}.
We have chosen to fit of our analytical model to the publicly available illustris simulations\footnote{ \url{https://www.tng-project.org/}}  because I) they have been shown to reproduce many of the \todo{geef concrete list (appendix other paper) } 
% The simulations were originally calibrated against the observed total cosmic star formation rate density and the stellar mass function of galaxies \citep{Pillepich2018}. They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018} and with observational constraints on the mass-metallicity relation of
% galaxies up to z = 2 \citep{Torrey+2019} as well as iron abundances \citep{FirstResTNG_Naiman2018} and
% the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}. These simulations have also already been used to make predictions for gravitational wave sources through pairing with  predictions for the outcomes of binary evaluation obtained with the BPASS code \citet{Briel+2021}.
global properties of galaxies and their scaling relations for a representative portion of the Universe \citep[e.g.][]{FirstResTNG_Naiman2018,Torrey+2021,Genel+2018,Hemler+2021}. 
II) \cite{Briel+2021} find that the \SFRDzZ from the EAGLE \citep{Schaye+2015,Crain+2015} and TNG simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients. 
% And III) the simulation output is publicly available.\footnote{ \url{https://www.tng-project.org/}} 
%
Although in this work, we only fit our model to the IllustrisTNG100 simulation, our prescription can be easily be used to fit other observational or simulated data of the metallicity dependent star formation rate density.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.

The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}. The stellar metallicity yields were updated with respect to the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}. %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}   
Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}. In particular, \cite{Briel+2021} find that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.

% Downsides of TNG100 
On the other hand, large uncertainties and crude approximations remain, also in the TNG simulations. For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated. Moreover, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} and binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} are ignored. Furthermore, the ionising background is turned on abruptly at $z=6$, again not accounting for the ionising contribution from stripped stars \citep[][]{Gotberg+2020,DoughtyFinlator2021}.

These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.
